Tweets

### 2020-05-21 Rmd/jse-2019-ms.Rmd
updated tweets document

From our collection of tweets, we chose to analyze those sent on five consecutive 
days from May 10, 2020 to May 14, 2020. We then submitted API queries to Twitter
to get the full content of tweets, including the tweet text.
We provide below the R code that we used to query the Twitter API to obtain full tweet content.

@@

Latent Dirichlet allocation models require that the corpus be inputted as a 
document by term matrix. Each row corresponds to a single document (a single 
tweet), and each column is a single term (or word). Each cell contains a 
count (the number of 
occurrences of a term in the specified document). We created a document by 
term matrix with the R functions `` from the `` R package.

>>>>

From our collection of tweets, we chose to analyze those sent on five consecutive 
days from May 10, 2020 to May 14, 2020. To minimize the computing requirements, we 
limited our study to tweets sent during a five-minute period (12:00pm to 12:05pm Eastern time) every day.
We then submitted API queries to Twitter
to get the full content of tweets, including the tweet text.
In supplementary files, we provide the R code that we used to query the Twitter API to obtain full tweet content.

@@

Latent Dirichlet allocation models require that the corpus be inputted as a 
document by term matrix. Each row corresponds to a single document (a single 
tweet), and each column is a single term (or word). Each cell contains a 
count (the number of 
occurrences of a term in the specified document). We created a document by 
term matrix with the R function `cast_dtm` from the `tidytext` package.

### 2020-05-21 Rmd/tweets-one.Rmd
updated tweets document

```{r, recover-{{date}}}
tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), 
                   col_names = FALSE)
```

## Dehydrate tweets for sharing

```{r, broken-{{date}}}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
```

## Hydrate tweets by querying Twitter

```{r, ids-{{date}}}
ids <- readr::read_csv(paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```

```{r, saveids-{{date}}}
# save ids of tweets that we actually used
readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv"), col_names = FALSE)
```

@@

```{r, stops-{{date}}}
# create a twitter-specific stop word list
remove_reg <- "&amp;|&lt;|&gt;"
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

@@

```{r, lda-{{date}}}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 8)
```

```{r, beta-{{date}}}
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

@@

```{r, plot-{{date}}}
tweets_top_terms %>%
  dplyr::mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip()
```

```{r, gamma-{{date}}}
tweets_gamma <- tidytext::tidy(tweets_lda, matrix = "gamma")
tweets_gamma
```

>>>>

```{r, recover-{{date}}}
fn <- paste0("../data/", {{date}}, "-analyzed-tweet-ids.csv")
tr_fn <- paste0("../data/", {{date}}, "-rehydrated-tweets.csv")
if (!file.exists(fn)){

  tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
  tweets %>%
    dplyr::select(status_id) %>%
    readr::write_csv(path = paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), 
                     col_names = FALSE)
  broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = trimws(format(status_id, scientific = FALSE)))
  ids <- readr::read_csv(paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), col_names = FALSE) %>%
    dplyr::rename(status_id = X1) %>%
    dplyr::mutate(status_id = as.character(status_id))
  tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                              parse = TRUE)
  tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
  tweets_rehydrated <- tweets_rehydrated1 %>%
    dplyr::bind_rows(tweets_rehydrated2)
  # save ids of tweets that we actually used
  readr::write_csv(tibble::as_tibble(tweets_rehydrated$status_id), path = fn, col_names = FALSE)
  readr::write_csv(tweets_rehydrated, path = tr_fn)
}
```

@@

@@

```{r, lda-{{date}}}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 8)
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

@@

```{r, plot-{{date}}}
tweets_top_terms %>%
  dplyr::mutate(term = tidytext::reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip() + 
  theme(axis.text.x = element_text(angle = 270))

```

```{r, ggsave-{{date}}}
ggplot2::ggsave(paste0("../results/beta-", {{date}}, ".png"))
```

### 2020-05-21 Rmd/tweets.Rmd
added files produced from tweets analysis
updated tweets document

1. Write a R script to query twitter streaming api to get 1 percent sample over 5'.
1. Demonstrate how to set up a crontab to execute script every 5'.
1. Verify that crontab approach works by running it on my computer for, say, 15'.
    1. Cautions about twitter databases: deletions and amendments to tweets
1. Examine structure of JSON obtained from api.

@@

@@

### Colophon

>>>>

1. Write a R script to query twitter streaming api to get 1 percent sample over 5'.
1. Demonstrate how to set up a crontab to execute script every 5'.
1. Cautions about twitter databases: deletions and amendments to tweets

@@

```{r, stops}
# create a twitter-specific stop word list
remove_reg <- "&amp;|&lt;|&gt;"
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

@@

## May 12, 2020

`r knitr::knit(text = out[[3]])`

## May 13, 2020

`r knitr::knit(text = out[[4]])`

## May 14, 2020

`r knitr::knit(text = out[[5]])`

## Colophon
